Sperm should evolve to make female meiosis fair.

### 2014-07-28 writeup_and_notes/GeneticsResub/male_dependent_drive.tex
yb minor changes for resub 7/28 (again)

Our theory also encourages phylogenetic hypotheses concerning the relationship between the opportunity 
	for female meiotic drive and the requirement of fertilization for the completion of female meiosis. 
For example, we predict that a lower opportunity for female meiotic drive,
        e.g. an animal lineage with a history of high inbreeding
        or selfing, 
        may be accompanied by a relaxation of the requirement of fertilization for the
        completion of female meiosis (although 
        opportunities to test this hypothesis may be limited because 
        %this effect may be weaks as such
        lineages may only persist for a short time). 
Our results also suggests that phylogenetic variation in the stage of female meiosis when
        fertilization occurs may influence the prevalence of  female meiotic drive.
For example, centromeric drive may be more common  in taxa where females complete MI before fertilization, 
	as compared to species in which sperm interact with eggs arrested  in MI, 
	because in the prior case sperm-based modifiers can only intercede during the second, but not the first  meiotic division. 
As a potential test of this hypothesis, the speed of centromere
	turnover could be compared in species in which sperm iteract with eggs paused at MI and MII 
	(assuming the pace of centromere turnover serves as a proxy for the frequency of MI drivers). 
\newline

>>>>

Our theory also encourages phylogenetic hypotheses concerning the relationship between the opportunity 
	for female meiotic drive and the requirement of fertilization for the completion of female meiosis. 
For example, we predict that a lower opportunity for female meiotic drive,
        e.g. an animal lineage with a history of high inbreeding
        or selfing, 
        may be accompanied by a relaxation of the requirement of fertilization for the
        completion of female meiosis (although 
        opportunities to test this hypothesis may be limited because 
        lineages may only persist for a short time). 
Our results also suggests that phylogenetic variation in the stage of female meiosis when
        fertilization occurs may influence the prevalence of  female meiotic drive.
For example, centromeric drive may be more common  in taxa where females complete MI before fertilization, 
	as compared to species in which sperm interact with eggs arrested  in MI, 
	because in the prior case, sperm-based modifiers can only intercede during the second, but not the first  meiotic division. 
As a potential test of this hypothesis, the speed of centromere
	turnover could be compared in species in which sperm interact with eggs paused at MI and MII 
	(assuming the pace of centromere turnover serves as a proxy for the frequency of MI drivers). 
\newline
